\documentclass[../bryan-hoang-cover-letter.tex]{subfiles}

\begin{document}
  % The company being applied to
  \recipient{Company Recruitment Team}{
    Kings Distributed Systems\\
    303 Bagot St., Suite 402\\
    Kingston, ON, K7L 5J9
  }

  % The title of the letter
  \lettertitle{Job Application for Software Developer}

  % How the letter is opened
  \letteropening{Dear Mr.\ Desjardins,}

  % Print the title with above letter informations
  \makelettertitle{}

  \begin{cvletter}
    I am an Applied Math and Engineering student at Queen's University with experience in software development living in Kingston. I am planning on graduating in May 2022 and would like to apply to work at Kings Distributed Systems (KDS) after that occurs.

    Most of my software development experience comes from working at KDS, where I had the opportunity to learn and work with various teams and work on several projects by myself. Working with the core development team, while following Agile software development practices, constituted the majority of my time as I learned the codebase and resolved tickets that the team needed to be done. I also worked on the Demo and Documentation websites in coordination with the marketing department, making decisions on some designs and the layout of each website. During the process, I quickly picked up working with various tools such as React and Sphinx, and would like to continue working on such projects.

    I am also experienced in communicating concepts for others to learn from. For instance, my time teaching and tutoring engineering students as a Teaching Assistant and EngLinks tutor helped me onboard new team members at KDS effectively. I helped cut down the average needed for onboarding to two days down from a week. I had an additional opportunity to help with outreach by presenting a workshop about the company's product at a Hackathon to over seventy students. Afterwards, I mentored other students at the hackathon, on one occasion networking with one who wanted to work at KDS\@.

    With the skills I have developed while working at KDS, I would like to continue to grow and contribute to the company's growth as a full-time software developer. With my development experience and communication skills, I am confident that I can contribute to the company's success.

    Thank you for your consideration. I would greatly appreciate getting another opportunity to work at KDS\@.
  \end{cvletter}
\end{document}
